Realistically Interesting Domains for Probabilistic Planners

### 2014-04-10 FinalPaper/paper.tex
todo changed

\begin{abstract}
	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains. By relaxing the definition of a dead-end, we argue that for many
real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.

@@

To evaluate FF-Replan and \textsc{Gourmand} in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature. These dynamics introduce large branching factors emphasizing the need for a planner to be scalable. To evaluate the model, the planner should also be sensitive to an expected reward maximization criterion.
Current finite horizon MDP problems as introduced in IPPC-11 are simplified and therefor do not account for the rich set of state-actions as would be available in a real-world planning problem. We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent. Using the baseline test introduced by Little et al.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.

@@

\todo{TODO maybe UAVs can be on or of too, so it's forced to use a further UAV.}
\todo{TODO what's also interesting is that Amazon.com uses drones for package deliveries}

@@

\subsection{Planning problems}

>>>>

\begin{abstract}

\todo{Rewrite abstract - Imara}

	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains. By relaxing the definition of a dead-end, we argue that for many
real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.

@@

\todo{rewrite problem formulation - Arian}
To evaluate FF-Replan and \textsc{Gourmand} in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature. These dynamics introduce large branching factors emphasizing the need for a planner to be scalable. To evaluate the model, the planner should also be sensitive to an expected reward maximization criterion.
Current finite horizon MDP problems as introduced in IPPC-11 are simplified and therefor do not account for the rich set of state-actions as would be available in a real-world planning problem. We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent. Using the baseline test introduced by Little et al.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.

@@

\myworries{maybe UAVs can be on or of too, so it's forced to use a further UAV.}

\myworries{what's also interesting is that Amazon.com uses drones for package deliveries}

@@

\todo{iterate on background - Imara}
\subsection{Planning problems}
